Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
references are ok now.

   \bibitem{b1} Business for society: how Siemens is changing life in Russia. Smart Energy. RBC, 2016 (in Russian). URL: http://siemens.rbc.ru/article1.html (access date: 05-15-2021)
   \bibitem{b2} Makarov E.B. Game forms of education. Open lesson. (in Russian) URL: https://openlesson.rf/articles/556327/ (access date: 05-15-2021)
   \bibitem{b3} Intelligent energy systems. Stand-simulator for programming and management of urban power networks. (in Russian) URL: http://polyus-nt.ru/powerstand.html (access date: 11/22/2021).
   \bibitem{b4} Chekan M.A. Development of a module for conducting virtual auctions for the training stand ST-IES LLC "Polyus-NT". Procs. of Wiener Readings - 2019: materials of the All-Russian Youth Scientific and Practical. conferences. - Irkutsk: Publishing house INRTU, 2019,  pp. 100-105. (in Russian)
   \bibitem{b5} Jia, W., Zhou, W. Distributed Network Systems: From Concepts to Implementations. Springer, USA, 2005, 513 p. ISBN: 9780387238395
   \bibitem{b6} Burns B. Designing Distributed Systems: Patterns and Paradigms for Scalable, Reliable Services. O'Reilly Media, Inc., Japan, 2018, 149 p. ISBN: 9781491983614
   \bibitem{b7} Raval S. Decentralized applications: harnessing Bitcoin's blockchain technology.  O'Reilly Media, Inc., USA, 2016. 103 p. ISBN: 9781491924549
   \bibitem{b8} Sunshine, C. A. Computer Network Architectures and Protocols., Springer US, 2013. 558 p. ISBN: 9781461308096
   \bibitem{b9} gRPC. URL: https://grpc.io (access date: 05-15-2021)
   \bibitem{b10} OAuth Community Site. URL: https://oauth.net (access date: 05-15-2021)
   \bibitem{b11} ORY Oathkeeper. GitHub. URL: https://github.com/ory/oathkeeper (access date: 05-15-2021)
   \bibitem{b12} NGINX.URL: https://nginx.org (access date: 03-21-2021)
   \bibitem{b13} Skorodumov A. Secure access to the company's information resources.  Information Security No. 2. URL:\url{http://lib.itsec.ru/articles2/sys_ogr_dost/bezopasnyy-dostup-k-informatsionnym-resursam-kompanii} (access date: 05-15-2021)
   \bibitem{b14} SSH Tunnel. SSH.COM URL:https://www.ssh.com/ssh/ tunneling/ (access date: 05-15-2021)
   \bibitem{b15} Users. OpenSSH URL: https://www.openssh.com/users.html (access date: 05-15-2021)
   \bibitem{b16} NTO (in Russian) URL: https://nti-contest.ru/ (access date: 05-20-2021)
   \bibitem{b17} Educational intensive "Island 10-21". Information Bureau 20.35 (in Russian) URL: https://ntinews.ru/event/obrazovatelnyy-intensiv-ostrov-10-21.html (access date: 05-20-2021)
   \bibitem{b18} Savvateev A.V., Filatov A.Yu. Theory and practice of auctions. Bulletin of the Voronezh State University. Series: Economics and Management. Voronezh, 2018. No. 3. P. 119-131. (in Russian)
   \bibitem{b19} Myerson R. Optimal auction design. Mathematics of Operations Research. 1981. Выпуск 6. № 1, С. 58-73. https://doi.org/10.1287/moor.6.1.58
   \bibitem{b20} RFC 6455 — The WebSocket Protocol. IETF URL: https://tools.ietf.org/html/rfc6455 (access date: 05-20-2021)
   \bibitem{b21} Concise Binary Object Representation : [сайт]. 2021. URL: https://cbor.io/ (access date: 20.05.2021)
   \bibitem{b22} Comparison of JSON Like Serializations. URL: http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/ (access date: 21.05.2021)
   \bibitem{b23} NixOS Linux. URL: https://nixos.org/ (access date: 05-15-2021)
   \bibitem{b24} Galatenko V.A., Dzabraev M.D., Kostyukhin K.A. Choosing a Package Manager for Multiversion Applications. Software products and systems. V. 31, No. 3, 2018. pp. 469–474. (in Russian) DOI: 10.15827/0236-235X.123.469-474.45
   \bibitem{b25} Haskell Language. : [сайт]. 2021. URL: https://haskell.org (access date: 20.05.2021)
   \bibitem{b26} Dhall configuration language, The : [сайт]. 2021. URL: https://dhall-lang.org/ (access date: 21.05.2021)
   \bibitem{b27} Bid Wars // Google Play [Электронный ресурс]. 2021. URL: https://play.google.com/store/apps/details?id=br.com.tapps.bid wars (access date: 05-15-2021)
   \bibitem{b28} TimeZero. MMORPG Handbook. Auction. (in Russian) URL: http://web.archive.org/web/20160325215014/ https://www.timezero.ru/manual/auction.ru.html (access date: 05-15-2021)
   \bibitem{b29} Sberbank-AST (in Russian) URL: http://www.sberbank-ast.ru/purchaseList.aspx (access date: 05-15-2021)
   \bibitem{b30} Titz O. Why TCP Over TCP Is A Bad Idea. URL: http://sites.inka.de/bigred/devel/tcp-tcp.html (access date: 21.05.2021)
   \bibitem{b31} Rapier C. et al. High performance SSH. SCP-HPN-SSH URL: http://www.psc.edu/networking/projects/hpn-ssh (access date: 21.05.2021)
   \bibitem{b32} Rapier C., Bennett B. High speed bulk data transfer using the SSH protocol. Proceedings of the 15th ACM Mardi Gras conference: From lightweight mash-ups to lambda grids: Understanding the spectrum of distributed computing requirements, applications, tools, infrastructures, interoperability, and the incremental adoption of key capabilities, 2008,  pp. 1-7. DOI: 10.1145/1341811.1341824
   \bibitem{b33} Hobbs, S. CORS Tutorial: A Guide to Cross-Origin Resource Sharing. Auth0. URL: https://auth0.com/ blog/cors-tutorial-a-guide-to-cross-origin-resource-sharing/ (access date: 21.05.2021)

>>>>

   \bibitem{b1} Business for society: how Siemens is changing life in Russia. Smart Energy. RBC, 2016 (in Russian). URL:\url{http://siemens.rbc.ru/article1.html} (access date: 05-15-2021)
   \bibitem{b2} E.~B.~Makarov. Game forms of education. Open lesson. (in Russian) URL:\url{https://openlesson.rf/articles/556327/} (access date: 05-15-2021)
   \bibitem{b3} Intelligent energy systems. Stand-simulator for programming and management of urban power networks. (in Russian) URL:\url{http://polyus-nt.ru/powerstand.html} (access date: 11/22/2021).
   \bibitem{b4} M.~A.~Chekan. Development of a module for conducting virtual auctions for the training stand ST-IES LLC "Polyus-NT". Procs. of Wiener Readings - 2019: materials of the All-Russian Youth Scientific and Practical. conferences. Irkutsk: Publishing house INRTU, 2019,  pp.~100-105. (in Russian)
   \bibitem{b5} W.~Jia, W.~Zhou. Distributed Network Systems: From Concepts to Implementations. Springer, USA, 2005, 513~p. ISBN: 9780387238395
   \bibitem{b6} Burns B. Designing Distributed Systems: Patterns and Paradigms for Scalable, Reliable Services. O'Reilly Media, Inc., Japan, 2018, 149~p. ISBN:~9781491983614
   \bibitem{b7} S.~Raval. Decentralized applications: harnessing Bitcoin's blockchain technology.  O'Reilly Media, Inc., USA, 2016. 103~p. ISBN:~9781491924549
   \bibitem{b8} C.~A.~Sunshine. Computer Network Architectures and Protocols. Springer US, 2013. 558~p. ISBN:~9781461308096
   \bibitem{b9} gRPC. URL:\url{https://grpc.io} (access date: 05-15-2021)
   \bibitem{b10} OAuth Community Site. URL:\url{https://oauth.net} (access date: 05-15-2021)
   \bibitem{b11} ORY Oathkeeper. GitHub. URL:\url{https://github.com/ory/oathkeeper} (access date: 05-15-2021)
   \bibitem{b12} NGINX. URL:\url{https://nginx.org} (access date: 03-21-2021)
   \bibitem{b13} A.~Skorodumov. Secure access to the company's information resources.  Information Security No.~2. URL:\url{http://lib.itsec.ru/articles2/sys_ogr_dost/bezopasnyy-dostup-k-informatsionnym-resursam-kompanii} (access date: 05-15-2021)
   \bibitem{b14} SSH Tunnel. URL:\url{https://www.ssh.com/ssh/ tunneling/} (access date: 05-15-2021)
   \bibitem{b15} Users. OpenSSH URL:\url{https://www.openssh.com/users.html} (access date: 05-15-2021)
   \bibitem{b16} NTO (in Russian) URL:\url{https://nti-contest.ru/} (access date: 05-20-2021)
   \bibitem{b17} Educational intensive ``Island 10-21''. Information Bureau 20.35. (in Russian) URL:\url{https://ntinews.ru/event/obrazovatelnyy-intensiv-ostrov-10-21.html} (access date: 05-20-2021)
   \bibitem{b18} A.~V.~Savvateev, A.~Yu.~Filatov A.Yu. Theory and practice of auctions. Bulletin of the Voronezh State University. Series: Economics and Management. Voronezh, 2018. No.~3. pp.~119-131. (in Russian)
   \bibitem{b19} R.~Myerson. Optimal auction design. Mathematics of Operations Research. 1981. volume~6. No.~1, pp.~58-73. \doi{10.1287/moor.6.1.58}
   \bibitem{b20} RFC 6455 — The WebSocket Protocol. IETF. URL:\url{https://tools.ietf.org/html/rfc6455} (access date: 05-20-2021)
   \bibitem{b21} Concise Binary Object Representation. URL:\url{https://cbor.io/} (access date: 20.05.2021)
   \bibitem{b22} Comparison of JSON Like Serializations. URL:\url{http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/} (access date: 21.05.2021)
   \bibitem{b23} NixOS Linux. URL:\url{https://nixos.org/} (access date: 05-15-2021)
   \bibitem{b24} V.~A.~Galatenko, M.~D.~Dzabraev, K.~A.~Kostyukhin. Choosing a Package Manager for Multiversion Applications. Software products and systems. volume~31, No.~3, 2018. pp.~469–474. (in Russian) \doi{10.15827/0236-235X.123.469-474.45}
   \bibitem{b25} Haskell Language. URL:\url{https://haskell.org} (access date: 20.05.2021)
   \bibitem{b26} Theh Dhall configuration language. URL:\url{https://dhall-lang.org/} (access date: 21.05.2021)
   \bibitem{b27} Bid Wars // Google Play [Электронный ресурс]. 2021. URL:\url{https://play.google.com/store/apps/details?id=br.com.tapps.bidwars} (access date: 05-15-2021)
   \bibitem{b28} TimeZero. MMORPG Handbook. Auction. (in Russian) URLs:\url{http://web.archive.org/web/20160325215014/}, \url{https://www.timezero.ru/manual/auction.ru.html} (access date: 05-15-2021)
   \bibitem{b29} Sberbank-AST (in Russian) URL:\url{http://www.sberbank-ast.ru/purchaseList.aspx} (access date: 05-15-2021)
   \bibitem{b30} O.~Titz. Why TCP Over TCP Is A Bad Idea. URL:\url{http://sites.inka.de/bigred/devel/tcp-tcp.html} (access date: 21.05.2021)
   \bibitem{b31} C.~Rapier et al. High performance SSH. SCP-HPN-SSH URL:\url{http://www.psc.edu/networking/projects/hpn-ssh} (access date: 21.05.2021)
   \bibitem{b32} C.~Rapier, B.~Bennett. High speed bulk data transfer using the SSH protocol. Proceedings of the 15th ACM Mardi Gras conference: From lightweight mash-ups to lambda grids: Understanding the spectrum of distributed computing requirements, applications, tools, infrastructures, interoperability, and the incremental adoption of key capabilities, 2008,  pp. 1-7. \doi{10.1145/1341811.1341824}
   \bibitem{b33} S.~Hobbs. CORS Tutorial: A Guide to Cross-Origin Resource Sharing. Auth0. URL:\url{https://auth0.com/blog/cors-tutorial-a-guide-to-cross-origin-resource-sharing/} (access date: 21.05.2021)
